DraftOne

### 2016-06-17 DraftOne.Rmd
Add figure with time trends

```{r}
#Make a sweet plot of these with n=1500 (just for fun, not working yet):
trendname <- c(rep("cos1", 1500), rep("cos2",1500), rep("cos3",1500), rep("linear",1500),  rep("curvilinear",1500), rep("cos1linear",1500))
trendtests <- c(calc_t(1500, trend = "cos1"), calc_t(1500, trend = "cos2"), calc_t(1500, trend = "cos3"), calc_t(1500, trend = "linear"), calc_t(1500, trend = "curvilinear"), calc_t(1500, trend = "cos1linear"))
trendframe <- data.frame(trendname, trendtests)
```

>>>>

Here's a plot of the trends:

```{r fig.width = 7, fig.height = 4}
library(dplyr)
library(tidyr)
library(ggplot2)

data.frame(day = 1:1000) %>%
  mutate(none = calc_t(n = 1000, trend = "no trend"),
         cos1 = calc_t(n = 1000, trend = "cos1"),
         cos2 = calc_t(n = 1000, trend = "cos2"),
         cos3 = calc_t(n = 1000, trend = "cos3"),
         linear = calc_t(n = 1000, trend = "linear"),
         curvilinear = calc_t(n = 1000, trend = "curvilinear"),
         cos1linear = calc_t(n = 1000, trend = "cos1linear")) %>%
  gather(trend_method, trend_value, -day) %>%
  ggplot(aes(x = day, y = trend_value)) + 
  geom_line() + facet_wrap(~ trend_method, ncol = 4) + 
  theme_bw()
```
